ESRC SDAI Application

### 2019-05-17 Draft.tex
update

@@

Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides. Our unique crime dataset will allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.

We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from this investigation can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

@@

 Hazard model?

>>>>

We first explore the characteristics of offenders and victims, focusing on gender, age and ethnicity.

@@

Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides. We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police and identify groups who are the least likely to report. We can contrast and validate these findings using our crime dataset.

Our unique crime dataset will further allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time. We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from this investigation can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

@@
